\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
Removed names from testin g sevction and mention instead user testing modified acknowledgements slightly to reflect content taken out of testing section.

For checking the correctness of \fs's generated spectrum generators
extensive unit tests against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
were done: We checked mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles and found all to agree within double machine
precision.  We also compared the overall pole mass spectrum after the
full fixed-point iteration has finished, and found the spectra to
agree at the sub-permille level.  Analytic tests of the $R$-symmetric
low-energy model, MRSSM, were done by Philip Diessner and several bugs
in SARAH were identified and fixed.

@@

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
introducing couplings with a single family index; Philip Diessner for
testing and identifying bugs in the MRSSM model file; Ulrik Günther
for compilation tests on Mac OS X and Dylan Harries for spotting
a bug in the configuration script.
%
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.

>>>>

To check the correctness of \fs's generated spectrum generators
extensive unit testing against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
was carried out. We checked mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles and found all to agree within double machine
precision.  We also compared the overall pole mass spectrum after the
full fixed-point iteration has finished, and found the spectra to
agree at the sub-permille level.

@@

In addition \fs has already undergone some user testing. This includes
analytic tests of the $R$-symmetric low-energy model (MRSSM) and
alternative E6 inspired SUSY scenarios.  The users who have helped us
with this are thanked in the acknowledgements.

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Philip Diessner
for testing and identifying several bugs in FlexibleSUSY and in SARAH,
in work on the MRSSM; Ulrik Günther for compilation tests on Mac OS X
and Dylan Harries for spotting a bug in the configuration script.
%
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.
